systemfit: A Package for Estimating\\ Systems of Simultaneous Equations in \proglang{R}

### 2006-10-01 paper/trunk/systemfit_compare_lm.tex
systemfit_compare_lm.tex: updated table of variables returned by systemfit due to revisions 335-349 of the systemfit package
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@698 591db2bd-e0a0-4d22-8c19-2192dbb7da31

\begin{table}[htbp]
\caption{Values returned by systemfit and lm}
\begin{tabular}{lll}
\hline
lm & systemfit & systemfit.equation \\
\hline
coefficients & coefficients & coefficients \\
residuals & & residuals \\
fitted.values & & fitted.values \\
rank & & \\
weights & & \\
df.residual & df.residual & df.residual \\
 & & df.residual.sys \\
call & call & \\
terms & & terms \\
contrasts & & \\
xlevels & & \\
offset & & \\
y** & & response* \\
x** & & modelMatrix* \\
 & & instMatrix* \\
model* & & modelFrame* \\
 & method & \\
 & eqnLabels & eqnLabel \\
 & nObs & nObs \\
 & nCoefAll & nCoefAll \\
 & nCoefEq & nCoef \\
 & nCoefLiAll & nCoefLiAll \\
 & nCoefLiEq & nCoefLi \\
 & iter & \\
 & bt & \\
 & bcov & covb \\
 & btcov & \\
 & rcov & \\
 & drcov & \\
 & rcovest & \\
 & olsr2 & r2 \\
 &  & adjr2 \\
 & mcelr2 & \\
 & R.restr & \\
 & q.restr & \\
 & TX & \\
 & control & \\
 & eq & \\
 & & inst \\
 & & ssr \\
 & & sigma \\
 & & \\
 & & \\
 & & \\
\hline
\end{tabular}
\end{table}

>>>>

\begin{table}[htbp]
\caption{Values returned by systemfit and lm}
\begin{tabular}{lll}
\hline
lm & systemfit & systemfit.equation \\
\hline
coefficients & coefficients & coefficients \\
residuals & & residuals \\
fitted.values & & fitted.values \\
rank & rank & rank \\
 & & rank.sys \\
 & & nCoef.sys \\
weights & & \\
df.residual & df.residual & df.residual \\
 & & df.residual.sys \\
call & call & \\
terms & & terms \\
contrasts & & \\
xlevels & & \\
offset & & \\
y** & & response* \\
x** & & modelMatrix* \\
 & & instMatrix* \\
model* & & modelFrame* \\
 & method & \\
 & & eqnLabel \\
 & iter & \\
 & bt & \\
 & bcov & covb \\
 & btcov & \\
 & rcov & \\
 & rcovest & \\
 & R.restr & \\
 & q.restr & \\
 & TX & \\
 & control & \\
 & eq & \\
 & & inst \\
 & & ssr \\
 & & sigma \\
\hline
\end{tabular}
\end{table}
